\section{
  \dl
    {Getting Started}
    {スタートアップガイド}
}

\subsection{\dl{Introductions}{イントロダクション}}



\qrdlink
  [\dl{This video shows how to create first simple patch using builtin modules.}{組み込みモジュールを使用して最初の簡単なパッチを作成する方法}]
  {https://youtu.be/BmG4IE_GD8c}
  {\dl{Introduction Video}{イントロダクションビデオ}}



\qrdlink[This video explains how wavetables and filters operate]
  {https://youtu.be/I24bB0UD4Qs}
  {\dl{Wavetable and Filter}{Wavetable and Filter}}



\qrdlink
  [\dl
    {
      Video showing use of:
      
      \underline{\nameref{section:modeuc}} - generates rhythm
      
      \underline{\nameref{section:modsmp}} for drums and VCO based bassline.
    }{
      \underline{\nameref{section:modeuc}} - generates rhythm
      
      \underline{\nameref{section:modsmp}} - および VCOベースのベースラインの使用方法}]
  {https://youtu.be/9D9-n-bAiTg}
  {Euclidean Dreams}



\qrdlink
  [\dl{Video showing use of arpeggiator to create chiptune sound}{アルペジエーターを使ってチップチューンサウンドを作る}]
  {https://youtu.be/oWMxbM7oF0Y}
  {Arpeggiator Chip Tune}

\qrdlink
  [\dl
    {
      Another wideo showing building patch from scratch using following modules:

      ARP (Arpeggiator) - sequences
      
      LFS (Shaper) - Rhythmic Modulation - bar size, 5 peaks - modulate filter
      
      GAT (Gater) - sequences Kick and Ride Cymbal to add some drum pattern
      
      DLY (Delay) - to enhance drums
      
      WTO (Wavetable) - with Unison and Detune creates wicked sound on FM table
      
      VCF (Biquad Low Pass) - just open and close cutoff to make simple oscillator move
      
      CLK (Clock) - added to LFS, ARP and GAT to control BPM of the whole track
    }
    {
      次のモジュールを使用してゼロからパッチを作成するアイデア
      
      \underline{\nameref{section:modarp}} - 全体のノートを配列
      
      \underline{\nameref{section:modlfs}} - Rhythmic Modulation - 1barの長さ - 5ピーク - フィルターをモジュレーション

      \underline{\nameref{section:modgat}} - キックとライドシンバルを配列して、ドラム パターンを追加

      \underline{\nameref{section:moddly}} - ドラムを強調

      \underline{\nameref{section:modwto}} - UnisonとDetuneで FM テーブルに邪悪なサウンドを作成

      \underline{\nameref{section:modvcf}} (Biquad Low Pass) - シンプルなオシレーターの動きを作るためのカットオフの開閉
      
      \underline{\nameref{section:modclk}} -  LFSに追加, トラック全体のBPMをコントロールするARPとGAT
    }
  ]
  {https://youtu.be/pmiCBfvZuS0}
  {\dl{Arpeggiator as Sequencer - Tutorial}{ArpeggiatorとSequencer - チュートリアル}}



\qrdlink
[\dl{Modulating Wavetables by LFO (internal modulation)}{ウエーブテーブルをLFOでモジュレート (内部モジュレーション)}]
{https://youtu.be/NmcN_rEX1P4}
{\dl{WTO and LFO Modulation}{WTOとLFOでモジュレーション}}

\qrdlink
[\dl{
  External Sequencer controls pitch of WTO

  WTO - Wavetable as Sound Source
  
  VCA - Amplifier
  
  ENV - Envelope for VCA  
}{
  外部シーケンサーでWTO のピッチを制御

  \underline{\nameref{section:modwto}} - サウンドソースとしてのWavetable
  
  \underline{\nameref{section:modvca}} - Amplifier
  
  \underline{\nameref{section:modenv}} - EVCAのエンベロープ
}]
{https://youtu.be/wP1mmZNP9xQ}
{\dl{Making Acid Bassline}{Acid basslineの作成}}




\subsection{\dl{Resources}{リソース}}

\dl{The Centre is a wavetable oscillator therefore it requires wavetables which are not supplied with the module. There is huge variety of resources online with free or paid high quality wavetables and shapes.
The shapes and wavetables can be downloaded from selected resources.}{The Centreはウェーブテーブルオシレーターであるため、ウェーブテーブルが必要ですが、モジュール内部には搭載されていません。そのため使用開始にあたってウェーブテーブルが必要です。無料または有料の高品質のウェーブテーブルとシェイプを備えた膨大な種類のリソースがオンラインにあります。 シェイプとウェーブテーブルは、選択したリソースからダウンロードできます。
}




\subsubsection{Wavetables}


\qrdlink{https://producerhive.com/ask-the-hive/what-are-wavetables/}
{\dl{ProducerHive Great Article on Wavetables +150 Wavetables FREE}{ProducerHive 150以上の高品質ウェーブテーブルがダウンロード可能}}



\qrdlink
  [Black Octopus Resources]
  {https://blackoctopus-sound.com/free-downloads/}
  {\dl{Freebies 2.5GB}{1.5GBの無料素材}}

\qrdlink
  [Black Octopus Resources]
  {https://blackoctopus-sound.com/product/stay-at-home-beats/}{Great Black Octopus tables}
  \qrdlink{https://www.youtube.com/watch?v=Nd5XV8Likz4}{Very nice and free sets of Wavetables}

\subsubsection{Shapes}
\qrdlink{https://databroth.gumroad.com/l/GRqHl}
{\dl{50 LFOs for Serum FREE by Databroth}{50の無料LFO。Serum用。}}
\qrdlink
  {https://psiger.gumroad.com/l/lfoshapes}
  {\dl{Get Into Shape by Psiger}{PsigerによるLFOシェイプ}}
% \qrdlink{https://discover.gumroad.com/?query=serum\%20shapes#hmhKd}{Shapes Resources at Gumroad}
